\documentclass[a4paper, 12pt]{article}
\title{SDP 2012 Performance Review 4}
\author{ Group 9 }
\date{}


\begin{document}
\maketitle

\begin{enumerate}
 \item \emph{Cristian Cobzarenco [9 points]}
  Written up the new Friendly Strategy and the Milestone 4 strategy, more improvements Vision and Control and fixed bugs in Simulator (mouse dragging).

 \item \emph{Callum Jamieson [7 points]}
  Worked on the new Friendly Strategy, implementing an algorithm for deciding where to kick based on opponent's position. A lot of testing with Control and Strategy.

 \item \emph{Kieran Doherty [6 points]}
  Worked some more on the Simulator, bugfixing and calibrating to get the simulator to be have more closely to reality.

 \item \emph{James Buckland [9 points]}
  Completely redesigned the robot, changing the size (to fit into the official requirements) and weight distribution, reduced the axle length. Constructed and tested multiple kicker designs. Worked with Slav Tomov.

 \item \emph{Slav Tomov [9 points]}
  Completely redesigned the robot, changing the size (to fit into the official requirements) and weight distribution, reduced the axle length. Constructed and tested multiple kicker designs Worked with James Buckland.

 \item \emph{Magda Sternik [6 points]}
  Continued work on updating the Communication protocol and brick-side code to include touch sensor functionality on the PC-side. Worked with Tymon Zgainski (pair programming).

 \item \emph{Tymon Zgainski [6 points]}
  Continued work on updating the Communication protocol and brick-side code to include touch sensor functionality on the PC-side. Worked with Magda Sternik (pair programming).

 \item \emph{Ronan Turner [0 points] }
  Not shown up these two weeks or answered our emails. We believe it is due to serious personal problems, since that was the last we heard from him.

 \item \emph{Brynach Jones [6 points] }
  He provided testing for Strategy and Control, before the friendly.

 \item \emph{Gavin Mann [0 points]}
  Still has not shown up.

\end{enumerate}


\end{document}